%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Vignesh Iyer                                 %
% MS CSE ASU                                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% -------------- README --------------
% Visit https://github.com/vgnshiyer/ASU-sparkysundevil-resume-template for comprehensive documenation.

% -------------- Resume ---------------
\documentclass{resume}

\begin{document}

% --------- Contact Information -----------
\introduction[
    fullname={Osama Hussein},
    email={itsosmx@gmail.com},
    phone={+201008815476},
    linkedin={linkedin.com/in/itsosmx},
    github={github.com/itsosmx}
]

% --------- Summary -----------
\summary{Senior computer science engineering student with experience developing full-stack websites, and mobile applications. I'm passionate about using technology to make a positive impact, and I'm committed to creating innovative solutions that enhance people's lives.}

% --------- Education ---------
\begin{educationSection}{Education}
    \educationItem[
        university={Nahda University, Bani Sweif, Egypt},
        college={Computer Science},
        graduation={Jun 2024},
        grade={3.12 GPA},
        program={B.S. in Computer Science},
        coursework={Software and Hardware Design Languages and Programmable Logic},
    ]
\end{educationSection}

% --------- Skills -----------
\begin{skillsSection}{Technical Skills}
    \skillItem[
        category={Frameworks},
        skills={NextJs, ReactJs, NodeJs, ExpressJs, React Native}
    ] \\
    \skillItem[
        category={Programming},
        skills={Javascript, Typescript, C\#, Python, HTML, CSS}
    ] \\
    \skillItem[
        category={Databases},
        skills={MongoDB, SQL}
    ] \\
    \skillItem[
        category={Certifications},
        skills={Udacity React Development Cross-Skilling certification – Nov 2022, Databases SQL Server and C\# - Feb 2021 }
    ]
\end{skillsSection}

% --------- Experience -----------
\begin{experienceSection}{Professional Experience}
    \experienceItem[
        company={Khamsat, Fiverr},
        location={Online},
        position={Freelancer},
        duration={May 2020 – Sept 2023}
    ]
    \begin{itemize}
        \itemsep -6pt {}
        \item Completed and delivered more than 80 projects for building Discord API bots using NodeJs
    \end{itemize}
\end{experienceSection}

% --------- Projects -----------
\begin{experienceSection}{Academic projects}
    \projectItem[
        title={Modern IOT Smart Home Automation Guard System},
        duration={Fall 2023 – Spring 2024},
        keyHighlight=Collaborated with a team of five to design and develop a smart home guard system with full control through a mobile application.
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
            \item Created a user-friendly React Native application for real-time data visualization, device control, and security alerts.
            \item Developed motion detection, window detection, and RFID-based security systems to manage and log access functionality, providing instant notifications and historical logging.
    \end{itemize}
\end{experienceSection}

% --------- Other work experience -----------
\begin{experienceSection}{Relevant Projects}
    \projectItem[
        title={Moltzim – Freelancer Platform},
        duration={June 2023 - Present},
        keyHighlight=Worked as a full stack developer to create a freelancer platform.
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
            \item Developed the frontend using Next.js and the backend with Node.js.
            \item Implemented real-time communication, admin dashboard, user dashboard, and payment integration.
    \end{itemize}
    \projectItem[
        title={The Ranch – Unity 3D Game},
        duration={July 2023 - Dec 2023},
        keyHighlight=Developed a complete game using Unity 3D and C\#.
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item Created a simulation game for ranchers managing animals and trading goods.
        \item Developed the game's AI behavior systems, trading, and auction systems.
    \end{itemize}
    \projectItem[
        title={Muslim Bank – Quran and Azkar Mobile App},
        duration={Jan 2023 - Feb 2023},
        keyHighlight=Built a mobile app to provide ad-free Quran and Azkar services.
        ]
        \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item Developed a media player for over 150 reciters, including the full Quran, prayer times, and Azkar.
        \item Enhanced skills in TypeScript and published the app on Google Play.
        \end{itemize}
\end{experienceSection}

% --------- Activities -----------
\begin{experienceSection}{Activities}
    \projectItem[
        title={ISF Innovation Catalyst Competition},
        keyHighlight={Porject manager and developer for Egyptian train system solution.},
        duration={Jun 2022 – Mar 2023}
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item Organized and managed a team of 11 members throughout the competition period team and assigned roles to every member
        \item Developed a user-friendly Kotlin application for real-time train tracking and ticket booking.
    \end{itemize}
\end{experienceSection}

\end{document}
